Figure 2. Bacterial Communities and Function

### 2022-01-30 reports/rmarkdown/manuscript/Figure2.Rmd
Fgure text update

### B
###################################
# WETT SMEAR BACTERIAL VALIDATION #
###################################
par(mar=c(1,5,4,1)) #b,l,t,r
x <- datasets_all_samples[["ASV_CVL_V3_normalized_batch_corrected"]]
xL <- rowsum(x , grepl("L.",rownames(x)) )[2,] / sum(grepl("L.",rownames(x)))
xM <- rowsum(x , grepl("Mobiluncus",rownames(x)) )[2,] / sum(grepl("Mobiluncus",rownames(x)))
xG <- rowsum(x , grepl("Gardnerella",rownames(x)) )[2,] / sum(grepl("Gardnerella",rownames(x)))

@@

barlist( data = rbind(WS=mL ,
                      "16S counts"=xL),
         genes = c("WS","16S counts"),
         clustering = group_annotation,srt=20,
         draw_mean_lines=F,col = pal)
mtext("Lactobacillus", side=3, las = 1, cex = .6, line = .5,xpd=T)
mtext("Wet Smear Bacteria Validation", side=3, las = 1, cex = .6, line =1.5,xpd=T, font = 2)

@@

image( t(top_picrust_data[h$order,][nrow(top_picrust_data):1,order(group_annotation[sample_use])]),
       col = colorRampPalette(c("navy","navy","grey95","firebrick4","firebrick4") )(99),
       breaks = seq(-5,5,length.out = 100),axes=F)
mtext("Differentialy Expressed KEGG Ontology Terms", side=3, las = 1, cex = .6, line =1.5,xpd=T, font = 2)
title(xlab="Study Groups", line=1)

>>>>

### B
###################################
# WET SMEAR BACTERIAL VALIDATION #
###################################
par(mar=c(1,5,4,1)) #b,l,t,r
x <- datasets_all_samples[["ASV_CVL_V3_normalized_batch_corrected"]]
xL <- rowsum(x , grepl("L.",rownames(x)) )[2,] / sum(grepl("L.",rownames(x)))
xM <- rowsum(x , grepl("Mobiluncus",rownames(x)) )[2,] / sum(grepl("Mobiluncus",rownames(x)))
xG <- rowsum(x , grepl("Gardnerella",rownames(x)) )[2,] / sum(grepl("Gardnerella",rownames(x)))

@@

barlist( data = rbind(WS=mL ,
                      "16S counts"=xL),
         genes = c("WS","16S counts"),
         clustering = group_annotation,srt=20,
         draw_mean_lines=F,col = pal)
mtext("Lactobacillus", side=3, las = 1, cex = .6, line = .5,xpd=T)
mtext("Wet Smear Bacteria Validation", side=3, las = 1, cex = .7, line =1.5,xpd=T, font = 2)

@@

image( t(top_picrust_data[h$order,][nrow(top_picrust_data):1,order(group_annotation[sample_use])]),
       col = colorRampPalette(c("navy","navy","grey95","firebrick4","firebrick4") )(99),
       breaks = seq(-5,5,length.out = 100),axes=F)
mtext("                        Differentially expressed KEGG Ontology terms and pathways", 
      side=3, las = 1, cex = .7, line =1.5,xpd=T, font = 2)
title(xlab="Study Groups", line=1)
